r5r: Rapid Realistic Routing with R5 in R

### 2020-09-15 r-package/paper2020/paper2020.Rmd
paper2020 - METHODS AND DATA section

p

>>>>

r5r has low data requirements, enabling routing analysis on 
different contexts wherever there is open data on street networks from 
OpenStreetMap (OSM). The package is also easily scalable allowing for fast 
computations at either the city or country level analysis. For multimodal 
transport routing, r5r will automatically combine OpenStreetMap with one or 
multiple public transport data sets in the stantard GTFS format to create a routable
transport network.

The r5r package has 3 fundamental functions. The `setup_r5()` function builds a 
multimodal transport network used for routing in R5. This function (1) 
downloads/updates a compiled JAR file of R5 and stores it locally in the r5r
package directory for future use; and (2) combines the OSM and GTFS data sets to
build a routable network object. For fast routing analysis, r5r currently has 
two functions:

- `travel_time_matrix`: a simple and fast function to efficiently compute travel
time estimates between one or multiple origin/destination pairs. The origin/destination
input can be either a spatial `sf POINT` object, or a `data.frame` containing the
columns `id`, `lon`, `lat.`

- `detailed_itineraries`:  function that provides the shortest or 
multiple alternative routes between origin/destination pairs. The output also 
brings detailed information for each route alternative at the trip segment level,
including the transport mode, waiting times, travel time and distance of each 
trip segment.

Both routing functions are versatile so users can easily can set customized inputs
such as transport mode, departure date and times, walking  an cycling speeds, 
maximum trip duration, walking distances or number of public transport transfers
etc.
